Using reference models in variable selection \vspace{.1in}

### 2020-04-26 paper/ref_approach.tex
fixed locfdr ref
bodyfat -> body fat

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{ll|rrrr}
%  \hline
Data  & Method & RMSE Full & RMSE Sel & \# Sel (CPL, AVG, SD) & \# Sel noisy (CPL, AVG, SD) \\ 
  \hline
bodyfat & projpred & 4.36 & 4.45 & (2, 2.3, 0.48) &   \\
& steplm & 4.38 & 4.46 & (7, 6, 0.94) &  \\
\hline
+ noisy variables & projpred & 4.48 & 4.46 & (2, 2, 0)&  (0, 0, 0)  \\
& steplm & 5.74 & 5.13 & (23, 26.2, 4.54) & (15, 18.9, 4.01) \\
%   \hline
\end{tabular}
\caption{Predictive performances with original bodyfat data (first two
  rows) and with extra noisy variables (last two rows) estimated with
  10-fold cross-validation. Abbreviations: RMSE = root mean squared error;
  Full = full model; Sel = selected submodel; 
  \# Sel = total number of selected variables;
  \# Sel noisy = number of selected noisy variables. 
  CPL = results for the complete data (not using cross-validation).
  AVG = average over the 10-fold cross-validation. SD = standard deviation
  over the 10-fold cross-validation.}
\label{tab:model_performances}
\end{table}

@@

In the bodyfat example above, our two simultaneous goals were to 
obtain good predictive performance and to select a smaller number of variables. 
When the goal is to select a minimal subset of variables,
which have similar predictive performance as the full model, we call it
\emph{minimal subset variable selection}. This minimal subset might
exclude variables which have some predictive information about the
target but, given the minimal subset, these variables are not able to
provide such additional information that would improve predictive
performance in a substantial manner.
The usual reason for this is that the relevant variables
which are not in the minimal subset are highly correlated with variables already in
the minimal subset. We will return to a problem of finding all
the variables with some predictive power in Section~\ref{complete-selection}.

@@

%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
\item steplm (without a reference model): Stepwise selection using AIC as in the bodyfat example.

@@

The control of the local false discovery rate consists of testing the
z-values $\{z_{j}\}_{j=1}^{p}$ of a normal mean problem (explained in Section \ref{simulations}) 
on whether they belong to the
theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$
meaning no relevance) against the alternative hypothesis distribution
$f_{1}$. In our case $f_{0}$ corresponds to the standard normal
distribution (see expression \eqref{eq:normal_means_problem2}). The
quantity of interest is the local false discovery rate (loc.fdr)
defined as: \
\begin{equation}
\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)},
\end{equation}
where $\pi_{0}$ is the prior probability of $H_0$ and
$f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal
distribution of the z-values. The latter is estimated using splines
with 7 degrees of freedom. We select variables with local false
discovery rate below $0.2$, which is suggested by
\citet{efron2012large} as it corresponds to a Bayes factor larger than
36 (assuming $\pi_{0}\geq0.9$). The results of the comparison are not
sensitive to the specific value. To estimate $\pi_{0}$ from the data,
we use the default setting provided by the \texttt{R}-package
\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr, Rlocfdr}.

>>>>

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{ll|rrrr}
%  \hline
Data  & Method & RMSE Full & RMSE Sel & \# Sel (CPL, AVG, SD) & \# Sel noisy (CPL, AVG, SD) \\ 
  \hline
body fat & projpred & 4.36 & 4.45 & (2, 2.3, 0.48) &   \\
& steplm & 4.38 & 4.46 & (7, 6, 0.94) &  \\
\hline
+ noisy variables & projpred & 4.48 & 4.46 & (2, 2, 0)&  (0, 0, 0)  \\
& steplm & 5.74 & 5.13 & (23, 26.2, 4.54) & (15, 18.9, 4.01) \\
%   \hline
\end{tabular}
\caption{Predictive performances with original body fat data (first two
  rows) and with extra noisy variables (last two rows) estimated with
  10-fold cross-validation. Abbreviations: RMSE = root mean squared error;
  Full = full model; Sel = selected submodel; 
  \# Sel = total number of selected variables;
  \# Sel noisy = number of selected noisy variables. 
  CPL = results for the complete data (not using cross-validation).
  AVG = average over the 10-fold cross-validation. SD = standard deviation
  over the 10-fold cross-validation.}
\label{tab:model_performances}
\end{table}

@@

In the body fat example above, our two simultaneous goals were to 
obtain good predictive performance and to select a smaller number of variables. 
When the goal is to select a minimal subset of variables,
which have similar predictive performance as the full model, we call it
\emph{minimal subset variable selection}. This minimal subset might
exclude variables which have some predictive information about the
target but, given the minimal subset, these variables are not able to
provide such additional information that would improve predictive
performance in a substantial manner.
The usual reason for this is that the relevant variables
which are not in the minimal subset are highly correlated with variables already in
the minimal subset. We will return to a problem of finding all
the variables with some predictive power in Section~\ref{complete-selection}.

@@

%Same as the data based Bayesian stepwise selection, but instead of using the observed data values to fit the models at each step, it uses the target values predicted by the reference model (which is the same as in the projpred approach).
\item steplm (without a reference model): Stepwise selection using AIC as in the body fat example.

@@

The control of the local false discovery rate consists of testing the
z-values $\{z_{j}\}_{j=1}^{p}$ of a normal mean problem (explained in Section \ref{simulations}) 
on whether they belong to the
theoretical null distribution $f_{0}$ (i.e., the null hypothesis $H_0$
meaning no relevance) against the alternative hypothesis distribution
$f_{1}$. In our case $f_{0}$ corresponds to the standard normal
distribution (see expression \eqref{eq:normal_means_problem2}). The
quantity of interest is the local false discovery rate (loc.fdr)
defined as: \
\begin{equation}
\text{loc.fdr}(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)},
\end{equation}
where $\pi_{0}$ is the prior probability of $H_0$ and
$f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal
distribution of the z-values. The latter is estimated using splines
with 7 degrees of freedom. We select variables with local false
discovery rate below $0.2$, which is suggested by
\citet{efron2012large} as it corresponds to a Bayes factor larger than
36 (assuming $\pi_{0}\geq0.9$). The results of the comparison are not
sensitive to the specific value. To estimate $\pi_{0}$ from the data,
we use the default setting provided by the \texttt{R}-package
\texttt{locfdr} \citep{Efron+Turnbull+Narasimhan:2015:locfdr}.
